Embedding to Reference t-SNE Space Addresses Batch Effects in Single-Cell Classification

### 2019-08-13 paper/policar2019-tsne-embedding.tex
Add missing references

We apply the proposed approach to t-SNE visualizations of
single-cell data. Data in this realm include a variety of
cells from specific tissues and are characterized through gene expression.
In our experiments, we considered several recently published data
sets where cells were annotated with the cell type. Our aim was to construct
t-SNE visualizations where similarly-typed cells would cluster together,
despite systematic differences between data sources. To that end, we focus
on comparing different ways of using t-SNE rather than differences to embeddings like PCA or MDS, which
have been substantially covered before~\todo{Add citation}. 
Below, we list the data sets,
describe single-cell specific data preprocessing procedures, and display the
resulting data visualizations. Finally, we discuss the success of the proposed
approach in alleviating the batch effects.

@@

Additional experiments with embedding secondary data sets from independent
studies are provided in the accompanying Python notebooks. We embedded brain
cells from~\cite{} to the reference embedding shown in
Fig.~\ref{fig:transform_brain}.a, and pancreas cells from~\cite{} to reference
in \ref{fig:transform_pancreas}.a. The conclusions are largely consistent, with the error rates 
of X\% and Y\%. \todo{Add errors}

>>>>

We apply the proposed approach to t-SNE visualizations of
single-cell data. Data in this realm include a variety of
cells from specific tissues and are characterized through gene expression.
In our experiments, we considered several recently published data
sets where cells were annotated with the cell type. Our aim was to construct
t-SNE visualizations where similarly-typed cells would cluster together,
despite systematic differences between data sources. To that end, we focus
on comparing different ways of using t-SNE rather than differences to embeddings like PCA or MDS, which
have been substantially covered before~\cite{tsne,umap_single_cell}. 
Below, we list the data sets,
describe single-cell specific data preprocessing procedures, and display the
resulting data visualizations. Finally, we discuss the success of the proposed
approach in alleviating the batch effects.

@@

Additional experiments with embedding secondary data sets from independent
studies are provided in the accompanying Python notebooks. We embedded brain
cells from Zeisel \etal~\cite{zeisel2015} to the reference embedding shown in
Fig.~\ref{fig:transform_brain}.a, and pancreas cells from Muraro \etal~\cite{muraro2016} to reference
in \ref{fig:transform_pancreas}.a. The conclusions are largely consistent, with the error rates 
of X\% and Y\%. \todo{Add errors}
